---
title: "diss_pilot_expt1_analysis"
author: "Katie"
date: "10/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lme4)
library(lmerTest) # p-values on lmer
source("summarySE.R")
library(corrplot)
library(plyr) # for ddply, calculating means for histograms
#library(ggpubr) # for balloon plot
library(apaTables) # for apa.cor.table


# differences in avgs btw groups
# hierarchical: differences btw groups, controlling for participant
```

```{r import data}
dir_proj <- here::here()
dir_data <- fs::path(dir_proj, "data")

df_v1n6 = read.csv(
  fs::path(dir_data, "2019-10-04_diss-pilot-expt1_df-users-items_v1n6.csv"),
  header=TRUE)

df_v2n48 = read.csv(
  fs::path(dir_data, "2019-10-31_diss-pilot-expt1_df-users-items_v2n48.csv"),
  header=TRUE)

df_v2n48_users = read.csv(
  fs::path(dir_data, "2019-10-31_diss-pilot-expt1_df-users-items_v2n48_users.csv"),
  header=TRUE)

df_v3n36 = read.csv(
  fs::path(dir_data, "2019-11-01_diss-pilot-expt1_df-users-items_v3n36.csv"), 
  header=TRUE)

df_v3n36_users = read.csv(
  fs::path(dir_data, "2019-11-01_diss-pilot-expt1_df-users-items_v3n36_users.csv"),
  header=TRUE)


# drop returned
df_v2n48_users <- filter(df_v2n48_users, status!="RETURNED") # 50
df_v3n36_users <- filter(df_v3n36_users, status!="RETURNED") # 37
df_v2n48 <- filter(df_v2n48, status!="RETURNED")
df_v3n36 <- filter(df_v3n36, status!="RETURNED")


# Create new dfs 

#TODO fix so no error; upon import, treating all text areas as factors instead of character vectors

v2columns <- c("effectivenessRestudy", "effectivenessGenerate", "chosenStrategy", "effectivenessChosenStrategy", "effort")
df_v2n48_users[,v2columns] <- as.factor(NA)
df_v2n48_v3n36_users = union(df_v2n48_users, df_v3n36_users)

df_v2n48[,v2columns] <- as.factor(NA)
df_v2n48_v3n36 = union(df_v2n48, df_v3n36)


# drop excluded 

# calculate summary stats across group
m_restudyScore <- mean(df_v2n48_v3n36_users$interventionStrategyRestudyScoreRound1, na.rm=T); m_restudyScore # 8.7
s_restudyScore <- sd(df_v2n48_v3n36_users$interventionStrategyRestudyScoreRound1, na.rm=T); s_restudyScore # 2

# drop at user level
df_v2n48_v3n36_users <- filter(df_v2n48_v3n36_users, interventionStrategyRestudyScoreRound1 >= m_restudyScore - 2*s_restudyScore)
df_v2n48_users <- filter(df_v2n48_users, interventionStrategyRestudyScoreRound1 >= m_restudyScore - 2*s_restudyScore)
df_v3n36_users <- filter(df_v3n36_users, interventionStrategyRestudyScoreRound1 >= m_restudyScore - 2*s_restudyScore)

# drop at item level
df_v2n48_v3n36 <- filter(df_v2n48_v3n36, prolificId %in% df_v2n48_v3n36_users$prolificId)
df_v2n48 <- filter(df_v2n48, prolificId %in% df_v2n48_users$prolificId)
df_v3n36 <- filter(df_v3n36, prolificId %in% df_v3n36_users$prolificId)

```

Now let's look at levenshtein distance as a scoring criteria. 

```{r examining exclusion criteria using levdist}

pids_r9 <- filter(df_v2n48_v3n36_users, interventionStrategyRestudyScoreRound1 <9)$prolificId
pids_ld1 <- filter(df_v2n48_v3n36_users, interventionStrategyRestudyScoreLevDist1 <9)$prolificId
pids_ld2 <- filter(df_v2n48_v3n36_users, interventionStrategyRestudyScoreLevDist2 <9)$prolificId
pids_ld3 <- filter(df_v2n48_v3n36_users, interventionStrategyRestudyScoreLevDist3 <9)$prolificId
pids_ld4 <- filter(df_v2n48_v3n36_users, interventionStrategyRestudyScoreLevDist4 <9)$prolificId
pids_ld5 <- filter(df_v2n48_v3n36_users, interventionStrategyRestudyScoreLevDist5 <9)$prolificId


filter(df_v2n48_v3n36, prolificId %in% pids_r9 & interventionStrategy=="restudy")[c(
  "prolificId", "itemEnglish", "interventionStrategyUserInputRound1", "interventionTestUserInput")]

filter(df_v2n48_v3n36, prolificId %in% pids_ld1 & interventionStrategy=="restudy")[c(
  "prolificId", "itemEnglish", "interventionStrategyUserInputRound1")]

```

Just looking at levDist 1 and levDist2, we see that there are lots of little typos that seem mostly correct

Does levDist1 and levDist2 score correlate better with restudyStrategy?

```{r correlations}

cor.test(df_v2n48_v3n36$interventionStrategyRestudyScoreRound1, df_v2n48_v3n36$interventionTestRestudyScore) # r=0.30
cor.test(df_v2n48_v3n36$interventionStrategyRestudyScoreRound1, df_v2n48_v3n36$interventionTestRestudyScoreLevDist1) # r=0.27
cor.test(df_v2n48_v3n36$interventionStrategyRestudyScoreRound1, df_v2n48_v3n36$interventionTestRestudyScoreLevDist2) # r=0.24

cor.test(df_v2n48_v3n36$interventionStrategyRestudyScoreRound1, df_v2n48_v3n36$assessmentTestScore) # r=0.35

#cor(studies1_2.filter.xy.strategy, use="complete.obs")
#factr4.cor.studies1_2.filter.xy.strategy = mat.sort(cor.strategy, f = fact.studies1_2.filter.xy.strategy.r4)
#corrplot(factr4.cor.studies1_2.filter.xy.strategy, tl.col='black', tl.cex=.75)

apa.cor.table(df_v2n48_v3n36[c(
  "interventionStrategyRestudyScoreRound1",
  "interventionTestRestudyScore",
  "interventionTestGenerateScore",
  "assessmentTestScore",
  "interventionTestRestudyScoreLevDist1",
  "interventionTestGenerateScoreLevDist1",
  "assessmentTestScoreLevDist1",
  "interventionTestRestudyScoreLevDist2",
  "interventionTestGenerateScoreLevDist2",
  "assessmentTestScoreLevDist2")])


corrplot.mixed(cor(df_v2n48_v3n36[c(
  "interventionStrategyRestudyScoreRound1",
  "interventionTestRestudyScore",
  "interventionTestGenerateScore",
  "assessmentTestScore",
  "interventionTestRestudyScoreLevDist1",
  "interventionTestGenerateScoreLevDist1",
  "assessmentTestScoreLevDist1",
  "interventionTestRestudyScoreLevDist2",
  "interventionTestGenerateScoreLevDist2",
  "assessmentTestScoreLevDist2")]), tl.col='black', tl.cex=.75)


```

Another metric: intervention effect
```{r intervention effect}
df_v2n48_v3n36_users$condition <- factor(df_v2n48_v3n36_users$condition,
                                         levels=c(0,1),
                                         labels=c("control", "expt"))

summary(lm(assessmentTestScore ~ condition, df_v2n48_v3n36_users))
summary(lm(assessmentTestScoreLevDist1 ~ condition, df_v2n48_v3n36_users))
summary(lm(assessmentTestScoreLevDist2 ~ condition, df_v2n48_v3n36_users))

summary(lm(assessmentTestScore ~ condition * interventionOutcome, df_v2n48_v3n36_users))
summary(lm(assessmentTestScoreLevDist1 ~ condition * interventionOutcome, df_v2n48_v3n36_users))
summary(lm(assessmentTestScoreLevDist2 ~ condition * interventionOutcome, df_v2n48_v3n36_users))


```
Plots
```{r intervention effect plots}
# means and errorbars, Assessment test score
melt <- tidyr::gather(df_v2n48_v3n36_users, key="measures", value="mean", assessmentTestScore, factor_key = TRUE) # factor_key preserves order
means <- summarySE(melt, measurevar="mean", groupvars=c("condition", "interventionOutcome", "measures"), na.rm=TRUE, conf.interval=0.95); means

filter(means, measures=="assessmentTestScore" & !is.na(interventionOutcome)) %>% ggplot(aes(interventionOutcome, mean)) + 
    geom_point(position=position_dodge(.9), stat="identity") + 
    geom_errorbar(aes(ymin=mean-ci, ymax=mean+ci), width=.2, position=position_dodge(.9)) + 
    theme(axis.text.x = element_text(angle = 90)) +
    labs(x = "assessmentTestScore") + facet_wrap(facet=vars(condition))

# means and errorbars, Assessment test score Levdist1
melt <- tidyr::gather(df_v2n48_v3n36_users, key="measures", value="mean", assessmentTestScoreLevDist1, factor_key = TRUE) # factor_key preserves order
means <- summarySE(melt, measurevar="mean", groupvars=c("condition", "interventionOutcome", "measures"), na.rm=TRUE, conf.interval=0.95); means

filter(means, measures=="assessmentTestScoreLevDist1" & !is.na(interventionOutcome)) %>% ggplot(aes(interventionOutcome, mean)) + 
    geom_point(position=position_dodge(.9), stat="identity") + 
    geom_errorbar(aes(ymin=mean-ci, ymax=mean+ci), width=.2, position=position_dodge(.9)) + 
    theme(axis.text.x = element_text(angle = 90)) +
    labs(x = "assessmentTestScoreLevDist1") + facet_wrap(facet=vars(condition))

# means and errorbars, Assessment test score Levdist2
melt <- tidyr::gather(df_v2n48_v3n36_users, key="measures", value="mean", assessmentTestScoreLevDist2, factor_key = TRUE) # factor_key preserves order
means <- summarySE(melt, measurevar="mean", groupvars=c("condition", "interventionOutcome", "measures"), na.rm=TRUE, conf.interval=0.95); means

filter(means, measures=="assessmentTestScoreLevDist2" & !is.na(interventionOutcome)) %>% ggplot(aes(interventionOutcome, mean)) + 
    geom_point(position=position_dodge(.9), stat="identity") + 
    geom_errorbar(aes(ymin=mean-ci, ymax=mean+ci), width=.2, position=position_dodge(.9)) + 
    theme(axis.text.x = element_text(angle = 90)) +
    labs(x = "assessmentTestScoreLevDist2") + facet_wrap(facet=vars(condition))

```


No...



Final decision, after meeting with Dan on 2019-12-13: No need to correct scores. Doesn't seem to make a difference.

